An algorithm for finding the global extremum\\ of a partially defined function\thanks{This work was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2023-11-15 2023/MMST/samplepaper.tex
change grant number

\begin{document}
%
\title{An algorithm for finding the global extremum\\ 
of a partially defined function\thanks{This work was supported by the Russian Science Foundation, project No. 21-11-00204.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Marina Usova\inst{1}\letter\orcidID{0000-0002-0722-6884} \and
Konstantin Barkalov\inst{1}\orcidID{0000-0001-5273-2471}}
%
\authorrunning{M. Usova, K. Barkalov}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Lobachevsky State University of Nizhny Novgorod, \\ Nizhny Novgorod, Russian Federation\\
\email{\{usova,konstantin.barkalov\}@itmm.unn.ru}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The paper discusses the problem of finding the global minimum of a function that may be partially defined in the search domain. The objective function may not be defined within some search regions due to the nature of the optimized object and of the simulation method (for example, numerical instability of the simulation method used). In some cases, these regions are known; but in most cases, the information about them is missing. The paper gives a description of a global search algorithm for solving such class of problems. Numerical experiments confirming the efficiency of the proposed algorithm were carried out.

>>>>

\begin{document}
%
\title{An algorithm for finding the global extremum\\ 
of a partially defined function\thanks{This work was supported by the Ministry of Science and Higher Education of the Russian Federation, project no. FSWR-2023-0034, and by the Research and Education Mathematical Center ``Mathematics for Future Technologies''.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Marina Usova\inst{1}\letter\orcidID{0000-0002-0722-6884} \and
Konstantin Barkalov\inst{1}\orcidID{0000-0001-5273-2471}}
%
\authorrunning{M. Usova, K. Barkalov}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Lobachevsky State University of Nizhny Novgorod, \\ Nizhny Novgorod, Russian Federation\\
\email{\{usova,konstantin.barkalov\}@itmm.unn.ru}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The paper discusses the problem of finding the global minimum of a function that may be partially defined in the search domain. The objective function may not be defined within some search regions due to the nature of the optimized object and of the simulation method (for example, numerical instability of the simulation method used). In some cases, these regions are known; but in most cases, the information about them is missing. The paper gives a description of a global search algorithm for solving such class of problems. Numerical experiments confirming the efficiency of the proposed algorithm were carried out.
